The effects of varying depth in cosmic shear surveys

### 2019-10-21 paperdraft.tex
added peter's suggestions

Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail. In particular, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.
\label{sec:calc of PS}

>>>>

Note that due to the statistical inhomogeneity of the field, many usually adapted conventions fail. In particular, $\langle \gamma(\theta)\gamma^*(\theta')\rangle$ does not only depend on the separation vector $\theta'-\theta$, but also on the position $\theta$. For example, the Fourier transform of the observed power spectrum yields $\langle \gamma(\b 0)\gamma^*(\b\theta)\rangle$, but not the shear correlation function.
\label{sec:calc of PS}
